### 2023-01-15 README.Rmd
make `resolve` default to resolve multiple pkgs fix #7
* implement granlist S3

The goal of gran (gran: R anachronism nullifier) [^gesis] is to obtain the dependency graph of an R package at a specific time point.

@@

```{r example}
library(gran)
rtoot_graph <- resolve(pkg = "rtoot", snapshot_date = "2022-12-31")
rtoot_graph
```

>>>>

The goal of gran (gran: R anachronism nullifier) [^gesis] is to obtain the dependency graph of R packages at a specific time point.

@@

```{r example}
library(gran)
graph <- resolve(pkgs = c("rtoot", "rtweet"), snapshot_date = "2022-12-31")
graph
```
